Ground state energy of quantum dots using the coupled cluster method

### 2018-06-05 project_2/article/article.tex
SCF

>>>>

            The neatest, yet arguably the most abstract, way to write the Hartree-Fock
            equations for electron $i$\footnote{This is weird, as electron
            should be indistinguishable and therefor impossible to label.} is
            \begin{equation}
                f_i \varphi_i = \varepsilon_i \varphi_i,
            \end{equation}               
            where $f_i$ is the Fock operator, $\varphi_i$ are eigenstates of the Fock 
            operator consiting of a set of one-electorn wave funcitons, called the
            Hartree-Fock molecular orbitals, and $\varepsilon_i$ are the eigenenergies
            of the Fock operator. The fock operator, in matrix notation, is given by
            \begin{equation}
                F_{pa} = H_{pq} +  J(D)_{pq} - \frac{1}{2}K(D)_{pq},
            \end{equation}
            where $h_i$ is the one-body operatore, while the two-body operator is 
            divided into what we call a direct part,
            \begin{equation}
                J(D)_{pq} = \braket{pq}{rs}D_{sr},
            \end{equation}
            and an exchange part,
            \begin{equation}
                K(D)_{pq} = \braket{ps}{rq}D_{sr}.
            \end{equation}
            The direct part of the two-body operator is comparable to classical Coloumb
            repulsion, while the exchange does not have a classical analog as it arises 
            from the antisymmetry requirement of the wavefunction. $D_{sr}$ is the 
            density matrix of the system.

            Introducing a basis set transforms the Hartree-Fock equations into the Rothaan
            equations
            \begin{equation}
                FC = SC\varepsilon.
            \end{equation}
            This is a generalised eigenvalue problem where $S$ serves as an overlap matrix
            that must be there in case of non-orthogonal basis. Since the Fock matrix $F$
            depends on it's own solution through the orbitals, the eigenvalue problem must
            be solved iteratively\footnote{This is also the reason why the
            Hartree-Fock-Roothaan equations are often called the self-consistent-field 
            procedure.}.
